Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-16 hscc2017/paper.tex
wording

For the majority of the benchmarks, the conjecture explained in
Section~\ref{synthesis-elements} holds and the two-stage verification 
engine is able to find a stable solution in less than one minute for half
of the benchmarks. This is possible if the inductive solutions need to be 
refined with few counterexamples and increments of the fixed-point precision.  
However, the benchmark \emph{SatelliteB2} with uncertainty ($G_{3b}$) has 
required too many counterexamples to refine its solution.  
For this particular case, the one-stage engine is able to complement the
two-stage approach and synthesize a solution instead.  It is important to
reiterate that the one-stage verification engine does not take advantage of
the inductive conjecture inherent to CEGIS, but instead fully explores the
counterexample space in one SAT instance.  As expected, this approach is 
significantly slower on average and is only useful for benchmarks where 
the CEGIS approach requires too many counterexample refinement iterations
such that exploring all counterexamples in a single SAT instance performs better.
Our results suggest an average performance difference of at least two orders
of magnitude between the two engines, leading to the one-stage engine timing
out on the majority of our benchmarks.  Table~\ref{tab:results}
lists the results for both engines, where in $16$ out of $23$
benchmarks, the two-stage engine is faster.

>>>>

For the majority of the benchmarks, the conjecture explained in
Section~\ref{synthesis-elements} holds and the two-stage verification engine
is able to find a stable solution in less than one minute for half of the
benchmarks.  This is possible if the inductive solutions need to be refined
with few counterexamples and increments of the fixed-point precision. 
However, the benchmark \emph{SatelliteB2} with uncertainty ($G_{3b}$) has
required too many counterexamples to refine its solution.  For this
particular case, the one-stage engine is able to complement the two-stage
approach and synthesizes a solution.  It is important to reiterate that the
one-stage verification engine does not take advantage of the inductive
conjecture inherent to CEGIS, but instead fully explores the counterexample
space in a single SAT instance.  As expected, this approach is significantly
slower on average and is only useful for benchmarks where the CEGIS approach
requires too many refinement iterations such that exploring all
counterexamples in a single SAT instance performs better.  Our results
suggest an average performance difference of at least two orders of
magnitude, leading to the one-stage engine timing out on the majority of our
benchmarks.  Table~\ref{tab:results} lists the results for both engines,
where in $16$ out of $23$ benchmarks, the two-stage engine is faster.
